\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgments}
I would like to take this opportunity to thank those who have supported me through the course of my PhD. First and foremost I would like to express my immense gratitude to the hepatorenal group at the \acl{SPMIC} and in particular my supervisor Professor Sue Francis who has guided me through the course of my PhD while also allowing me to shape the project into one that I have such enthusiasm for.

%Work social
I would also like to show my appreciation for the wider community at work, be that support scanning, synchronised swearing at software, stimulating seminars or simply a willingness to have a nap in the scanner at three in the afternoon (thankfully many of the protocols in this thesis are respiratory triggered so finding volunteers to be scanned has never been difficult). % Change to hard if you need to avoid an extra line

A PhD is never easy, writing up during a pandemic induced lockdown even less so. The last few years and in particular the closing months of my PhD would not have been the same without my friends at \acs{SPMIC}, TEC and ONBI, be that in person over a pint or at the other end of a video call. 

%Family
Last, but by no means least, thanks are due to my family. My parents were called in to meet with a primary school teacher who was disappointed with my performance in science. The teacher explained that I had just drawn squiggles when the class was asked to draw what made us individual. Thankfully, despite my atrocious art skills, my parents recognised the double helices of DNA and saw fit to encourage my enjoyment of science, otherwise my life could have followed a very different path.